\chapter*{ \begin{center} 
    \textbf{\LARGE ABSTRACT}  % Large, bold, and centered heading  
\end{center} }  
\addcontentsline{toc}{chapter}{ABSTRACT}  
\vspace{-2cm}  % Adjust this value if needed to reduce space further  
 

 The Top Score Quiz System is a comprehensive web-based application developed to automate and manage online assessments and quizzes efficiently. The system provides a centralized platform for educational institutions and organizations to create, manage, and evaluate quizzes seamlessly without the overhead of traditional paper-based methods. It replaces manual evaluation processes with an automated grading system, thereby improving operational efficiency, reducing human errors, and enhancing the overall learning experience.
\\\\
The application implements role-based access control to ensure secure interaction among users such as Admin, Teacher, and Student. The Admin module oversees user management and system integrity. Teachers can create dynamic quizzes, add multiple-choice or true/false questions, and monitor student performance in real-time. Students can join quizzes using a unique access code, participate in timed assessments, and view their immediate results and detailed reviews upon completion.
\\\\
A key feature of the system allows teachers to bulk upload questions using CSV formats and share quiz access codes easily. Developed using the Laravel framework with a MySQL database, the system ensures data security, scalability, and high performance. By centralizing the assessment workflow and digitizing academic evaluations, the Top Score Quiz System significantly improves administrative efficiency and supports modern educational practices.\\\\
